---
title: "Schedule"
output:
  html_document:
    toc: false
---

Here's the plan for the semester:
\

```{r, include = FALSE}
library(kableExtra)
library(tidyverse)
library(DT)
library(lubridate)
```


```{r include = FALSE}
start_date <- lubridate::as_date("2019-09-03")
end_date <- lubridate::as_date("2019-12-12")
dur_weeks <- (start_date %--% end_date) %/% weeks(1)
meet_days <- c("Monday", "Wednesday", "Friday")

# gets the first monday from any date
# https://stat.ethz.ch/pipermail/r-help/2011-September/288846.html
first_monday <- function(x) {
  as.Date(cut(x, "weeks"))
}

by_meeting <- function(x, meet_on = c("Monday",
                                      "Tuesday",
                                      "Wednesday",
                                      "Thursday",
                                      "Friday",
                                      "Saturday",
                                      "Sunday")) {
  meet_on <- match.arg(meet_on, several.ok = TRUE)
  week_of <- first_monday(x)
  numeric_days <- wday(first_monday(x))
  # options: M/Tu/W/Th/Fri/Sat/Sun
  here <- make_date(day = meet_on, 
                    month = month(week_of), 
                    year = year(week_of))
  enframe(here, name = "class_num", value = "date")
}

#' takes start_date as input
make_meets_numeric <- function(x = start_date, 
                               meet_on = c("Monday",
                                      "Tuesday",
                                      "Wednesday",
                                      "Thursday",
                                      "Friday",
                                      "Saturday",
                                      "Sunday")) {
  meet_on <- match.arg(meet_on, several.ok = TRUE)
  # make first week of dates
  first_week <- first_monday(x) + days(0:6)
  # subtract from start_date to get numbers from those
  lookup <- tibble(
    numbers = (x %--% first_week) / days(1),
    days = as.character(wday(first_week, label = TRUE, abbr = FALSE))
  )
  # construct week one from first_monday plus days
  week_one <- x
  days_we_meet <- c()
  # get month and year from start_date
  # I know that Monday is first_monday + 0, Tuesday is first_monday + 1
  )

cal_by_week <- tibble(
  week_of = begin_week(start_date) + weeks(1:dur_weeks),
  week_num = rep(1:dur_weeks),
  date_day = start_date + weeks(1:dur_weeks),
  week_day = wday(date_day, label = TRUE)
)

cal_by_meet <- tibble(
  week_of = rep(begin_week(start_date) + weeks(1:dur_weeks), each = 2),
  week_num = rep(1:dur_weeks, each = 2)
)
```

break it down:

1. I need to construct a full "fake" first_week
  - Input:
    - first_date (can be any date in first week)
    - first_date --> first_monday
    - first_monday --> first_week (a full week of actual real dates)
1. I need to construct a real first week
  - Input:
    - days of the week that meet (as characters)
    - first_week (from above)
    - week_one <- starting from the first_monday + days(c(1, 4)) # where days is a number
1. I need to construct the full calendar
  - Input:
    - week_one (a full week of just dates of meetings)
    - duration (number of weeks to repeat the pattern in week_one)

```{r, echo = FALSE}
schedule <- tribble(~Week, ~Weekday, ~Date, ~Topic,  ~Slides, ~slides_url, ~Labs, ~labs_url,
                "1", "Tues", "Sep 3", "Welcome", "Slides", "01-slides-welcome.html", "", "",
                "1", "Thurs", "Sep 5", "Data Viz I", "Slides", "02-slides-data-viz-I.html", "", "",
                "2", "Tues", "Sep 10", "Data Viz II", "Slides", "03-slides-topic.html", "", "",
                "2", "Thurs", "Sep 12", "Topic 3", "Slides", "03-slides-topic.html", "Lab 1", "lab1.html",
                "3", "Tues", "Sep 17", "Topic 4", "Slides", "03-slides-topic.html", "", "",
                "3", "Thurs", "Sep 19", "Topic 5", "Slides", "03-slides-topic.html", "", "",
                "4", "Tues", "Sep 24", "Topic 6", "Slides", "03-slides-topic.html", "", "",
                "4", "Thurs", "Sep 26", "Topic 7", "Slides", "03-slides-topic.html", "Lab 2", "lab2.html",
                "5", "Tues", "Oct 1", "Topic 8", "Slides", "03-slides-topic.html", "", "",
                "5", "Thurs", "Oct 3", "Topic 9", "Slides", "03-slides-topic.html","", "",
                "6", "Tues", "Oct 8", "Topic 10", "Slides", "03-slides-topic.html","", "",
                "6", "Thurs", "Oct 10", "Topic 11", "Slides","03-slides-topic.html", "Lab 3", "lab3.html",
                "7", "Tues", "Oct 15", "Topic 12", "Slides", "03-slides-topic.html","", "",
                "7", "Thurs", "Oct 17", "Topic 13", "Slides", "03-slides-topic.html","", "",
                "8", "Tues", "Oct 22", "Topic 14", "Slides", "03-slides-topic.html","", "",
                "8", "Thurs", "Oct 24", "Topic 15", "Slides", "03-slides-topic.html","Lab 4", "lab4.html",
                "9", "Tues", "Oct 29", "Topic 16", "Slides", "03-slides-topic.html","", "",
                "9", "Thurs", "Oct 31", "Topic 17", "Slides", "03-slides-topic.html","", "",
                "10", "Tues", "Nov 5", "Topic 18", "Slides", "03-slides-topic.html","", "",
                "10", "Thurs", "Nov 7", "Topic 19", "Slides", "03-slides-topic.html","Lab 5", "lab5.html",
                "11", "Tues", "Nov 12", "Topic 20", "Slides", "03-slides-topic.html","", "",
               "11", "Tues", "Nov 19", "Topic 21", "Slides", "03-slides-topic.html","", "",
                "12", "Thurs", "Nov 26", "Topic 22", "Slides", "03-slides-topic.html","", "",
                "12", "Tues", "Nov 28", "Thanksgiving - No Class", "", "","", "",
                "13", "Thurs", "Dec 3", "Topic 23", "Slides", "03-slides-topic.html","Lab 6", "lab6.html",
                "13", "Tues", "Dec 5", "Topic 24", "Slides", "03-slides-topic.html","", "",
                "14", "Thurs", "Dec 10", "Review", "", "","", "",
                "14", "Tues", "Dec 12", "Final Exam", "", "","", "",
               )
             
 schedule %>% 
  mutate(
    Labs = cell_spec(Labs, "html", link = labs_url),
    Slides = cell_spec(Slides, "html", link = slides_url)) %>%
  dplyr::select(-ends_with("_url")) %>%
    datatable(escape = FALSE) 

 

```

